### 2013-07-24 appa.tex
Meeting Tanya in 20 minutes oops.
Before meeting Ben.

% This is appa.tex
%
% This file is for appendices.  If you don't have any appendices, delete
% the percent sign from the beginning of the next line.
%\endinput

@@

\section{Title of Appendix}

Appendices may appear after the paper proper.  Appendices may hold
extra information that would interrupt the flow of the paper and that
is not absolutely necessary for the reader to appreciate the work.
For example, a large number of related figures or a mathematical
derivation could go nicely in an appendix.

>>>>

% This is appa.tex
%
% This file is for appendices.  If you don't have any appendices, delete
% the percent sign from the beginning of the next line.
\endinput

@@

\section{Casework for Theorem \ref{thm:count_maps}}
\label{appa:count_maps}
Compute like hell.

### 2013-07-24 paper.tex
Before meeting Ben.

\section{Preliminaries and Definitions}
NOTE: If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dashed for readability.

@@

First, we need a criteria to determine the top.  Fortunately, this is extremely easy.
\begin{definition*}
	For a binary string $\ul b$, let $\pi_1(\ul b)$ denote the number of $1$'s in $\ul b$, and $\pi_0(\ul b)$ the number of $0$'s.
\end{definition*}
\begin{proposition}
	For any $\ul b$ of length $n$, \[
		\Top_{\SS_n} \ul b =
		\begin{cases}
			\varnothing & \text{if } \pi_1(\ul b) \equiv 0 \pmod{2} \\
			s & \text{if } \pi_1(\ul b) \equiv 1 \pmod{2} \\
		\end{cases}.
		\]
\end{proposition}
\begin{proof}
	Straightforward induction on $n$.  
\end{proof}

Subsequently, we make the following definition.
\begin{definition*}
	For a binary string $\ul b$, define the \emph{partial-sum string} of $\ul b$, denoted $\ul b^\ast$, as follows:
	\[
		\ul b^\ast [i] = 
		\begin{cases}
			1 & \text{if } b[1] + b[2] + \dots + b[i] \equiv 1 \pmod{2} \\
			0 & \text{otherwise}
		\end{cases}.
	\]
\end{definition*}
This lets us state our main result for this section.
\begin{theorem}
	If $\ul a, \ul b \in \BB_n$ obey $\Top_{\SS_n} \ul a = \Top_{\SS_n} \ul b$, then
	\[
		\MM_{\SS_n} \left( \ul a, \ul b \right)
		=
		\begin{cases}
			0 & \text{if }\ \exists 1 \le i \le n-1:\ \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}
		\end{cases}.
	\]
\end{theorem}
\begin{figure}[ht]
	\centering
	\begin{asy}
		size(7cm);
		real h = 0.7;
		pen s = blue, t = red + dashed + 0.6;
		pen dot_s = blue, dot_t = red;
		int n = 8;
		draw(currentpicture, (0,0)--(0,h/2)..((0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
		draw(currentpicture, (1,0)--(1,h/2)..((1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
		draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
		draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
		draw(currentpicture, (4,0)--(4,h), s);
		dot(currentpicture, (4,h), dot_s);
		draw(currentpicture, (7,0)--(7,h), s);
		dot(currentpicture, (7,h), dot_s);
		dot(currentpicture, (1, h/2), dot_s);
		dot(currentpicture, (2, h/2), dot_s);
		label(currentpicture, "1", (0,-1.5h), dir(90));
		label(currentpicture, "s", (0,-0.8*h), dir(90));
		label(currentpicture, "0", (1,-1.5h), dir(90));
		label(currentpicture, "s", (1,-0.8*h), dir(90));
		label(currentpicture, "0", (2,-1.5h), dir(90));
		label(currentpicture, "s", (2,-0.8*h), dir(90));
		label(currentpicture, "1", (3,-1.5h), dir(90));
		label(currentpicture, "s", (3,-0.8*h), dir(90));
		label(currentpicture, "0", (4,-1.5h), dir(90));
		label(currentpicture, "s", (4,-0.8*h), dir(90));
		label(currentpicture, "1", (5,-1.5h), dir(90));
		label(currentpicture, "s", (5,-0.8*h), dir(90));
		label(currentpicture, "1", (6,-1.5h), dir(90));
		label(currentpicture, "s", (6,-0.8*h), dir(90));
		label(currentpicture, "0", (7,-1.5h), dir(90));
		label(currentpicture, "s", (7,-0.8*h), dir(90));
	\end{asy}
	\caption{A half-map with base $\SS_8$.}
	\label{fig:pf_trivial_theorem_example}
\end{figure}
\begin{proof}
	We will only consider the case where $\Top \ul a = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.  See figure \ref{fig:pf_trivial_theorem_example} for a example of such a map.

	Number the anchors $1$, $2$, $\dots$ from left to right.

	For a half-map $\MM(\ul b)$, define the \emph{antennae} of a connected component to be the anchors which it touches.  Note that the antennae always form a single contiguous sequence of anchors.

	Now, we observe that for each $1 \le i \le n-1$, we have that $\ul a^\ast[i] = 1$ if and only if $i$ and $i+1$ are both antennae of some component.

@@

\begin{definition*}
	Let $R(\ul r)$ denote the $\ul r$ with any consecutive blocks of $s$'s replaced by a single $s$, and similarly for $t$.
\end{definition*}
For example, $R(sststttts) = ststs$.

\begin{theorem}
	Let $\ul r$ be an expression of length $\ell$, and suppose $R(\ul r) = \AA_n$.
	\begin{enumerate}
		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{\ell-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r} \ul b$.
		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{\ell-n} \binom{2k-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r} \ul b$.
	\end{enumerate}
	\label{thm:count_maps}
\end{theorem}
Of course, if $\ul r$ begins with the character $t$, then one can simply reverse the roles of $s$ and $t$ in the above theorem to obtain an analogous formula.

@@

\begin{proof}[Proof of Theorem \ref{thm:count_maps}]
	First we will resolve the case where $\ul r = \AA_n$.  This follows basically immediately by induction on $n$.  
\end{proof}

@@

In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
\begin{theorem}[Bubble Theorem]
	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar, whose color is opposite that of the bubble.
	\label{thm:bubble}
\end{theorem}
\begin{theorem}[Caterpillar Theorem]
	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
	\label{thm:caterpillar}
\end{theorem}
\begin{theorem}[Pasture Theorem]
	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then:
	\begin{enumerate}[(i)]
		\ii Pastures $1$ through $N-1$ contain either nothing or a free component.
		\ii Pasture $N$ contains nothing if $T[N] \neq \AA_n[n]$, and contains a single caterpillar otherwise.
	\end{enumerate}
	\label{thm:pasture}
\end{theorem}

@@

	Next, it is easy to verify that all caterpillars held inside $B$ are red, otherwise this contradicts the construction of Libedinsky's light leaves.  Then let $S$ be the set of anchors contained on the boundary of any caterpillars held inside $B$ (in a sense, on the ``outermost'' level).

	Define a pair of red anchors $u, v \in S$ to be \emph{quasi-connected} if one can draw an arc from $u$ to $v$ contained entirely in one half-map which does not intersect any boundaries of $B$, and furthermore, there is no other pair of red anchors both between $u$ and $v$, inclusive, with this property.

	Now we claim that \textbf{any quasi-connected pair of red anchors is actually joined by a single arc}.  To prove this, take such a quasi-connected pair $u$ and $v$.  Now we'll focus only on the half-map in which the prescribed arc is drawn.  We thus may state that an arc \emph{shields} any anchors between its endpoints.

	\begin{figure}[ht]
		\centering
		\begin{asy}
			size(6cm);
			pen s = blue, t = red + dashed + 0.6;
			pen dot_s = blue, dot_t = red;
			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
			draw((1,0)..(3,2)..(5,0), t); // red covering arc
			draw((2,0)..(3,1)..(4,0), s); // blue covering arc again
			label("$u$", (3,0), dir(-90));
			label("$v$", (5,0), dir(-90));
		\end{asy}
		\hspace{2em}
		\begin{asy}
			size(6cm);
			pen s = blue, t = red + dashed + 0.6;
			pen dot_s = blue, dot_t = red;
			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
			draw((1,0)..(4,2)..(7,0), t); // red covering arc
			draw((2,0)..(4,1)..(6,0), s); // blue covering arc
			label("$u$", (3,0), dir(-90));
			label("$v$", (5,0), dir(-90));
		\end{asy}
		\caption{Proving the bubble theorem with quasi-connected vertices.}
		\label{fig:pf_bubble}
	\end{figure}
	Because the string is alternating, there exists a blue anchor between $u$ and $v$, say $x$.  Furthermore, there must be some blue arc (of $B$) shielding $u$ and $v$.  By the light-leave construction, there must be some red arc $A$ covering $x$.  If this arc joins $u$ and $v$, then we are done.  Otherwise, it must completely cover either $u$ or $v$ (by quasi-connectedness).  Now we have two cases,
	\begin{itemize}
		\ii If the arc covers exactly one of $u$ or $v$, say $u$, then there must be a blue arc shielding $u$ from $A$.  But then this contradicts the quasi-connectedness, because now it is not possible to join $u$ and $v$ by an arc on this half-map.  This case is illustrated by the left half of figure \ref{fig:pf_bubble}.
		\ii If the arc covers both $u$ and $v$, then there must be a blue arc which shields both $u$ and $v$, which is itself shielded by $A$.  Then we can repeat the same procedure with this new blue arc.  This case is illustrated by the left half of figure \ref{fig:pf_bubble}.
	\end{itemize}
	Therefore any pair of quasi-connected anchors must be connected by an arc.  However, it is evident that this implies there is a path of arcs joining any pair of red anchors.  Therefore all red anchors in $S$ must be connected.  So there is a single caterpillar, as desired.
\end{proof}

@@

	We perform induction on the size of the caterpillar. 
	If there are no bubbles, then the caterpillar is simply a barbell (because it is a tree, which contracts to a barbell).
	This is the base step.
	For the inductive step, consider an arbitrary bubble.  Inside it is exactly one caterpillar, say $c$, by the Bubble Theorem.  Because the original caterpillar has nesting level $0$, we deduce $c$ is merely a barbell, and hence is either $\alpha_s$ or $\alpha_t$.
	Applying the barbell-forcing rule of equation \eqref{eq:barbell_break} generates two terms.  One of them is zero because it creates a new empty bubble. The other the original diagram with the cycle cut open and the contents removed, multiplied by one of $\left\{ x,y \right\}$.  The inductive hypothesis now applies directly, and this completes the first induction.

@@

\subsection{Proof of the Pasture Theorem}

\section{A Recursion for the Alternating Case}
In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.

>>>>

\section{Preliminaries and Definitions}
\textbf{Note:} If possible, this document should be printed in color.  However, I have left blue lines as solid and red lines as dashed for readability.

@@

First, we need a criteria to determine the top.  Fortunately, this is extremely easy.
\begin{definition*}
	For a binary string $\ul b$, let $\pi_1(\ul b)$ denote the number of $1$'s in $\ul b$, and $\pi_0(\ul b)$ the number of $0$'s.
\end{definition*}
\begin{proposition}
	For any $\ul b$ of length $n$, \[
		\Top_{\SS_n} \ul b =
		\begin{cases}
			\varnothing & \text{if } \pi_1(\ul b) \equiv 0 \pmod{2} \\
			s & \text{if } \pi_1(\ul b) \equiv 1 \pmod{2} \\
		\end{cases}.
		\]
	\label{prop:s_top}
\end{proposition}
\begin{proof}
	Straightforward induction on $n$.  
\end{proof}

Subsequently, we make the following definition.
\begin{definition*}
	For a binary string $\ul b$, define the \emph{partial-sum string} of $\ul b$, denoted $\ul b^\ast$, as follows:
	\[
		\ul b^\ast [i] = 
		\begin{cases}
			1 & \text{if } \ul b[1] + \ul b[2] + \dots + \ul b[i] \equiv 1 \pmod{2} \\
			0 & \text{otherwise}
		\end{cases}.
	\]
\end{definition*}
This lets us state our main result for this section.
\begin{theorem}
	If $\ul a, \ul b \in \BB_n$ obey $\Top_{\SS_n} \ul a = \Top_{\SS_n} \ul b$, then
	\[
		\MM_{\SS_n} \left( \ul a, \ul b \right)
		=
		\begin{cases}
			0 & \text{if }\ \exists 1 \le i \le n-1:\ \ul a^\ast[i] = \ul b^\ast[i] = 1 \\
			\alpha_s^{n - \pi_1(\ul a^\ast) - \pi_1(\ul b^\ast) - \ul a^\ast[n]} & \text{otherwise}
		\end{cases}.
	\]
	\label{thm:s_eval}
\end{theorem}
\begin{figure}[ht]
	\centering
	\begin{asy}
		size(7cm);
		real h = 0.7;
		pen s = blue, t = red + dashed + 0.6;
		pen dot_s = blue, dot_t = red;
		int n = 8;
		draw(currentpicture, (0,0)--(0,h/2)..((0+1)/2.0,h*1)..(1,h/2)--(1,0), s);
		draw(currentpicture, (1,0)--(1,h/2)..((1+2)/2.0,h*1)..(2,h/2)--(2,0), s);
		draw(currentpicture, (2,0)--(2,h/2)..((2+3)/2.0,h*1)..(3,h/2)--(3,0), s);
		draw(currentpicture, (5,0)--(5,h/2)..((5+6)/2.0,h*1)..(6,h/2)--(6,0), s);
		draw(currentpicture, (4,0)--(4,h), s);
		dot(currentpicture, (4,h), dot_s);
		draw(currentpicture, (7,0)--(7,h), s);
		dot(currentpicture, (7,h), dot_s);
		dot(currentpicture, (1, h/2), dot_s);
		dot(currentpicture, (2, h/2), dot_s);
		label(currentpicture, "1", (0,-1.5h), dir(90));
		label(currentpicture, "s", (0,-0.8*h), dir(90));
		label(currentpicture, "0", (1,-1.5h), dir(90));
		label(currentpicture, "s", (1,-0.8*h), dir(90));
		label(currentpicture, "0", (2,-1.5h), dir(90));
		label(currentpicture, "s", (2,-0.8*h), dir(90));
		label(currentpicture, "1", (3,-1.5h), dir(90));
		label(currentpicture, "s", (3,-0.8*h), dir(90));
		label(currentpicture, "0", (4,-1.5h), dir(90));
		label(currentpicture, "s", (4,-0.8*h), dir(90));
		label(currentpicture, "1", (5,-1.5h), dir(90));
		label(currentpicture, "s", (5,-0.8*h), dir(90));
		label(currentpicture, "1", (6,-1.5h), dir(90));
		label(currentpicture, "s", (6,-0.8*h), dir(90));
		label(currentpicture, "0", (7,-1.5h), dir(90));
		label(currentpicture, "s", (7,-0.8*h), dir(90));
	\end{asy}
	\caption{A half-map with base $\SS_8$.}
	\label{fig:pf_trivial_theorem_example}
\end{figure}
\begin{proof}
	We will only consider the case where $\Top \ul a = \varnothing$, so that $\ul a^\ast[n] = \ul b^\ast[n] = 0$; the other case is essentially identical.  See figure \ref{fig:pf_trivial_theorem_example} for a example of such a map.

	Number the anchors $1$, $2$, \dots from left to right.

	For a half-map $\MM(\ul b)$, define the \emph{antennae} of a connected component to be the anchors which it touches.  Note that the antennae of a component always form a single contiguous sequence of anchors.

	The key observation is that for $1 \le i \le n-1$, we have that $\ul b^\ast[i] = 1$ if and only if $i$ and $i+1$ are both antennae of some component in $\MM(\ul b)$.  This follows by construction.

@@

\begin{definition*}
	Let $R(\ul r)$ denote $\ul r$ with any consecutive blocks of $s$'s replaced by a single $s$, and similarly for $t$.
\end{definition*}
For example, $R(sststttts) = ststs$.

\begin{theorem}
	Let $\ul r$ be an expression of length $\ell$, and suppose $R(\ul r) = \AA_n$.
	\begin{enumerate}[(i)]
		\ii If $n=2k+1$ is odd, then for each $0 \le m \le k$, there are $2^{\ell-n} \binom{2k}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m}$, $\AA_{2m-1}'$, and $\AA_{2m}'$ as $\Top_{\ul r} \ul b$.
		\ii If $n=2k$ is even, then for each $0 \le m \le k-1$, there are $2^{\ell-n} \binom{2k-1}{m+k}$ binary strings $\ul b$ yielding each of $\AA_{2m+1}$, $\AA_{2m+2}$, $\AA_{2m}'$, and $\AA_{2m+1}'$ as $\Top_{\ul r} \ul b$.
	\end{enumerate}
	\label{thm:count_maps}
\end{theorem}
Of course, if $\ul r$ begins with the character $t$, then one can simply reverse the roles of $s$ and $t$ in the above theorem to obtain an analogous formula.

@@

\begin{proof}[Proof of Theorem \ref{thm:count_maps}]
	First we will resolve the case where $\ul r = \AA_n$, so that $\ell = n$ and $2^{\ell-n} = 1$.  This follows by induction on $n$.  The main idea is that, for the binary strings of length $n$, we consider those that end with $1$ and those that end with $0$.  Those that end with a $0$ have the same top when the trailing $0$ is deleted, whilst those with end bit $1$ have a top which differs by one character if the trailing $1$ is deleted.  We simply check that in all eight cases, the binomial coefficients add up to give the new binomial coefficients (via Pascal's identity).  The computation is left to a reader.

	To complete the theorem, we note that we can treat each consecutive block of $s$'s of length $m$ as a single $s$, where there a $2^{m-1}$ ways to get a $1$ and $2^{m-1}$ ways to get a $0$.  (This follows from Proposition \ref{prop:s_top}.)  This reduces to the previous case $\ul r = \AA_n$, but with some extra factors of $2$; aggregating all of them yields the factor of $2^{\ell-n}$, as desired.
\end{proof}

@@

In this section we will show several results which show that the possible outputs of a map with base $\AA_n$ are extremely restricted.  We present them below, before providing proofs of each.
\begin{theorem}[Bubble Theorem]
	Consider a bubble in a full-diagram with base $\AA_n$.  The bubble holds exactly one caterpillar, whose color is opposite that of the bubble.
	\label{thm:bubble}
\end{theorem}
\begin{theorem}[Caterpillar Theorem]
	Any caterpillar in a full-diagram with base $\AA_n$ evaluates in the form $x^my^n\alpha_s$ if it is blue, or $x^my^n\alpha_t$ is red.
	\label{thm:caterpillar}
\end{theorem}
\begin{theorem}[Pasture Theorem]
	Consider a full-diagram with $N+1$ pastures (numbered $0$, $1$, \dots, $N$) with base $\AA_n$ and top $T$.  Suppose further that $N \ge 1$ (or equivalently, $T \neq \varnothing$).  Then:
	\begin{enumerate}[(i)]
		\ii Pastures $1$ through $N-1$ contain either nothing or a free component.
		\ii Pasture $N$ contains nothing if $T[N] = \AA_n[n]$, and contains a single caterpillar otherwise.
	\end{enumerate}
	\label{thm:pasture}
\end{theorem}

@@

	Next, it is easy to verify that all caterpillars held inside $B$ are red, otherwise this contradicts the construction of Libedinsky's light leaves.

	Define a pair of red anchors $u, v$, with $u$ to the left of $v$, to be \emph{quasi-connected} if (i) one can draw an arc from $u$ to $v$ contained entirely in one half-map which does not intersect blue lines, and (ii) there is no red anchor $w$ strictly between $u$ and $v$ for which one can draw a similar arc on the same half-map joining $w$ and $v$.

	Now we claim that \textbf{any quasi-connected pair of red anchors is actually joined by a single arc}.  To prove this, take such a quasi-connected pair $u$ and $v$.  Now we'll focus only on the half-map in which the prescribed arc is drawn.  We thus may state that an arc \emph{shields} any anchors which lie between its endpoints.

	\begin{figure}[ht]
		\centering
		\begin{asy}
			size(6cm);
			pen s = blue, t = red + dashed + 0.6;
			pen dot_s = blue, dot_t = red;
			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
			draw((1,0)..(3,2)..(5,0), t); // red covering arc
			draw((2,0)..(3,1)..(4,0), s); // blue covering arc again
			label("$u$", (3,0), dir(-90));
			label("$v$", (5,0), dir(-90));
		\end{asy}
		\hspace{2em}
		\begin{asy}
			size(6cm);
			pen s = blue, t = red + dashed + 0.6;
			pen dot_s = blue, dot_t = red;
			for (int i=0; i<=8; i+=2) { dot( (i,0), dot_s ); }
			for (int i=1; i<=8; i+=2) { dot( (i,0), dot_t ); }
			draw((0,0)..(1,2)..(3,4)..(5,3)..(6,5)..(7,2)..(8,0), s);
			draw((1,0)..(4,2)..(7,0), t); // red covering arc
			draw((2,0)..(4,1)..(6,0), s); // blue covering arc
			label("$u$", (3,0), dir(-90));
			label("$v$", (5,0), dir(-90));
		\end{asy}
		\caption{Proving the bubble theorem with quasi-connected vertices.}
		\label{fig:pf_bubble}
	\end{figure}
	Because the string is alternating, we can take a blue anchor $x$ immediately to the left of $v$.  Now, there must be some blue arc shielding $u$ and $v$ (since $u,v$ are inside a blue bubble).  By the light-leave construction, there must be some red arc $A$ covering $x$.  If this arc joins $u$ and $v$, then we are done.  
	Otherwise, if it has endpoint $v$ then it must completely cover $u$ by condition (ii) of quasi-connectedness; if not, then it must completely cover $v$.  This leads us to two cases.
	\begin{itemize}
		\ii If the arc covers exactly one of $u$ or $v$, say $u$, then there must be a blue arc shielding $u$ from $A$.  But then this contradicts the quasi-connectedness, because now it is not possible to join $u$ and $v$ by an arc on this half-map.  This case is illustrated by the left half of figure \ref{fig:pf_bubble}.
		\ii If the arc covers both $u$ and $v$, then there must be a blue arc which shields both $u$ and $v$, which is itself shielded by $A$.  Then we can repeat the same procedure with this new blue arc.  This case is illustrated by the right half of figure \ref{fig:pf_bubble}.
	\end{itemize}
	Therefore any pair of quasi-connected anchors must be connected by an arc.  However, one can verify that the red anchors in $B$ but not in any other blue bubble are ``connected'' under quasi-connectedness.\footnote{That is, one can follow a sequence of red anchors, each consecutive pair quasi-connected, from any red anchor to any other red anchor.}  Therefore all such red anchors must be connected.  So there is a single caterpillar, as desired.
\end{proof}

@@

	We perform induction on the size of the caterpillar. 
	If there are no bubbles, then the caterpillar is simply a barbell (because it is a tree, which contracts to a barbell).
	This is the base step.
	For the inductive step, consider an arbitrary bubble.  Inside it is exactly one caterpillar, say $c$, by the Bubble Theorem.  Because the original caterpillar has nesting level $0$, we deduce $c$ is merely a barbell, and hence is either $\alpha_s$ or $\alpha_t$.
	Applying the barbell-forcing rule of equation \eqref{eq:barbell_break} generates two terms.  One of them is zero because it creates a new empty bubble. The other is the original diagram with the cycle cut open and the contents removed, multiplied by one of $\left\{ x,y \right\}$.  The inductive hypothesis now applies directly, and this completes the first induction.

@@

\subsection{Proof of the Pasture Theorem}
\begin{figure}[ht]
	\centering
	\begin{asy}
		size(11cm);
		real h = 0.7;
		pen s = blue, t = red + dashed + 0.6;
		pen dot_s = blue, dot_t = red;
		int n = 6;

		picture before;
		draw(before, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
		draw(before, (2,0)--(2,h), s);
		dot(before, (2,h), dot_s);
		draw(before, (5,0)--(5,h), t);
		dot(before, (5,h), dot_t);
		draw(before,(0,0)--(0,3*h), s);
		draw(before,(3,0)--(3,3*h), t);
		draw(before,(4,0)--(4,3*h), s);
		dot(before, (3, h/2), dot_t);

		add(before); add(reflect((0,0),(1,0))*before);
		draw((-1,0)--(6,0));

		picture after;
		draw(after, (1,0)--(1,h/2)..((1+3)/2.0,h*2)..(3,h/2)--(3,0), t);
		draw(after, (4,0)--(4,h/2)..((4+6)/2.0,h*2)..(6,h/2)--(6,0), s);
		draw(after, (3,0)--(3,h/2)..((3+7)/2.0,h*4)..(7,h/2)--(7,0), t);
		draw(after, (0,0)--(0,h/2)..((0+8)/2.0,h*5.5)..(8,h/2)--(8,0), s);
		draw(after, (2,0)--(2,h), s);
		dot(after, (2,h), dot_s);
		draw(after, (5,0)--(5,h), t);
		dot(after, (5,h), dot_t);
		dot(after, (3, h/2), dot_t);

		add(shift((9,0)) * after);
		add(shift((9,0)) * reflect((0,0),(1,0))*after);
		draw((8,0)--(18,0));

		label("$\to$", (7,0));
	\end{asy}
	\caption{In the first diagram, $\ul a = \ul b = 110010$.  In the second, $\ul a' = \ul b' = 110010111$.  Closing the pastures allows us to deduce the Pasture Theorem from the Bubble Theorem.}
	\label{fig:pf_pasture}
\end{figure}
The bubble theorem and the pasture theorem are structurally very similar.  In fact, we will now show a somewhat surprising proof that the Pasture Theorem follows from the Bubble Theorem.
\begin{proof}[Proof of Theorem \ref{thm:pasture}]
	Again, let $T$ denote the top, with length $N$.  In the first case, suppose $T[N] \neq \AA_n[n]$; that is, the last characters of $T$ and $\AA_n$ differ.  Then it must be the case that the rightmost anchor is not part of a fence.
	Now suppose the map arose from $\MM_{\AA_n}(\ul a, \ul b)$.  Let $\ul a'$ be the string formed by appending $N$ $1$'s to $\ul a$, and define $\ul b'$ similarly.  Now consider the map \[ \MM_{\AA_{n+N}} \left( \ul a', \ul b' \right). \]  See figure \ref{fig:pf_pasture} for an example.

	It is easy to verify that the top of this new map is zero.  Now what we have done is enclose the contents of each pasture into bubbles.  The Bubble Theorem tells us that the innermost bubble can have exactly one caterpillar, while the other bubbles must contain only a single caterpillar, which was once a fence.  This implies the Pasture Theorem in the first case.

	The case where $T[N] = \AA_n[n]$ is similar.  We simply append a zero followed by $N$ $1$'s and repeat the same procedure.  The only difference is that the innermost barbell was generated by the $0$ we appended, and thus was not part of the original diagram.
\end{proof}

\section{A Recursion for the Alternating Case}
In this section we present a limited recursion for computing $\MM_{\AA_n}(\ul a, \ul b)$.  This recursion is sufficient to calculate $\MM_{\AA_n}(\ul b, \ul b)$.
TODO: Write this.
